---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  warning = FALSE,
  message = FALSE
)
``` 

# About `lalonde` 

[![Travis-CI Build Status](https://travis-ci.org/jjchern/lalonde.svg?branch=master)](https://travis-ci.org/jjchern/lalonde)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jjchern/lalonde?branch=master&svg=true)](https://ci.appveyor.com/project/jjchern/lalonde)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/lalonde)](https://cran.r-project.org/package=lalonde)

The Lalonde datasets are widely used in the causal inference literature. The current package aims for easing the process of loading such datasets in R. I found myself calling the following command 

```R
haven::read_dta("http://www.nber.org/~rdehejia/data/nsw_dw.dta")
```

in several R projects. It might be easier to just type `lalonde::nsw_dw`.

# Data Source

- All the datasets are available in `txt` and `dta` format from Dehejia's [website](http://users.nber.org/~rdehejia/nswdata2.html)

# Installation

```R
# install.packages("devtools")
devtools::install_github("jjchern/lalonde")
```

# Usage

The datasets print nicely in the tidyverse:

```{r}
library(tidyverse)

lalonde::nsw

lalonde::nsw_dw
```

